\textls[-15]{\thetitle \mbox{(Technical Report)}}

### 2022-06-24 coq-example.tex
Adding more info for "accessing family field"

\subsection{Type Safety for STLC}
We start with the very basic type safety proof of STLC, largely adapted from Software Foundation~\cite{pierce2014software}, which is also one of the primal motivating example of this project.

>>>>

\subsection{Type Safety for STLC}\EDJ{We need a fuller view of the two examples. Especially show "accessing family components outside that family".}
We start with the very basic type safety proof of STLC, largely adapted from Software Foundation~\cite{pierce2014software}, which is also one of the primal motivating example of this project.

### 2022-06-24 lang-design.tex
Adding more info for "accessing family field"

First and foremost, we don't want to throw away some basic good properties from Coq. \textlabel{Req (0A)}{langdesign-req0}~\textbf{we want to retain the incremental(modular) type checking}. Notice that, the modularity here in Coq is a bit different from other language, because Coq is \textit{interactive} theorem proving so we actually need \textit{statement-wise} incremental type checking, not only for saving the compilation time, but also for the immediate feedback and type-checking for the Coq developer. We don't want our family to ruin this conventional routine of interactive development. \textlabel{Req (0B)}{langdesign-req0b}~\textbf{we also want to keep the computational property of Coq when use family}. Coq, as a constructive logic, has been famous for its ability to do calculations and extract programs. We don't want our Family facility to ruin this: the developers should be able to project field as first-class value just like Coq's Module.

>>>>

First and foremost, we don't want to throw away some basic good properties from Coq. \textlabel{Req (0A)}{langdesign-req0}~\textbf{we want to retain the incremental(modular) type checking}. Notice that, the modularity here in Coq is a bit different from other language, because Coq is \textit{interactive} theorem proving so we actually need \textit{statement-wise} incremental type checking, not only for saving the compilation time, but also for the immediate feedback and type-checking for the Coq developer. We don't want our family to ruin this conventional routine of interactive development. \textlabel{Req (0B)}{langdesign-req0b}~\textbf{we also want to keep the computational property of Coq when use family}. Coq, as a constructive logic, has been famous for its ability to do calculations and extract programs. We don't want our Family facility to ruin this: the developers should be able to project field from families as first-class value just like how we can treat fields of Coq's Module as first-class values.

### 2022-06-24 syntactic-example.tex
Adding more info for "accessing family field"

@@

>>>>

The resulting constructed families are $\goodTerm{\cdot}{}{}$

@@

Finally we make some comments on how a family is encoded in our metatheory. A family object will have a signature that expose the type of fields and the details of inductive type . This exposure can make sure inheritance can override and inherit field correctly. Sealing is only hiding information \textbf{inside one family}, i.e. hiding information of the former fields for the later fields, and thus the later fields is defined on the abstract interface of the former fields. The signature will expose the sealing itself and the inductive type. (See $"sig"_5$ has all the sealing information and inductive definition). A former sealing might not be related to any later sealing, for example, $"sig"_3$ is constructed using $"sl"_1$ but $"sig"_4$ is using trivial sealing $id_s$.
